\begin{enumerate}

  \item The transitive property of equality says that if $a=b$ and $b=c$
  then $a=c$.
  Does the implication arrow satisfy a transitive property?
  If so, state it.
  
  等式的传递性表明，如果 $a=b$ 且 $b=c$，那么 $a=c$。蕴含箭头是否满足传递性？如果满足，请陈述之。
  \wbvfill
  
  \hint{
  I sometimes like to rephrase the implication $X \implies Y$ as ``X's truth forces Y to be true.''  Does that help?
  If we know that X being true forces Y to be true, and we also know that Y being true will force Z to be true, what can we conclude?
  
  我有时喜欢将蕴涵 $X \implies Y$ 改写为“X的真迫使Y为真。”这有帮助吗？如果我们知道X为真迫使Y为真，并且我们也知道Y为真将迫使Z为真，我们能得出什么结论？
  \vfill
  
  }
  
  \item Complete truth tables for the compound sentences $A \implies B$ and
    ${\lnot}A \lor B$.
  
  完成复合句 $A \implies B$ 和 ${\lnot}A \lor B$ 的真值表。
  \wbvfill
    
  \hint{
  You should definitely be able to do this one on your own, but anyway, here's an outline of the table:
  
  你绝对应该能自己完成这个，但无论如何，这里是表格的框架：
  
  \begin{tabular}{|c|c|c|c|} \hline
  \rule[-6pt]{0pt}{24pt}  $A$ & $B$ & $A \implies B$ & ${\lnot}A \lor B$ \\ \hline
  \rule[-6pt]{0pt}{24pt}  $T$ &  $T$ & & \\ \hline
  \rule[-6pt]{0pt}{24pt}  $T$ & $\phi$ & & \\ \hline	 	 
  \rule[-6pt]{0pt}{24pt}  $\phi$ & $T$ & & \\ \hline
  \rule[-6pt]{0pt}{24pt}  $\phi$ & $\phi$ & & \\ \hline
  \end{tabular}
  
  \vfill
  
  }
  \workbookpagebreak
  
  \item Complete a truth table for the compound sentence $A \implies (B \implies C)$ and for the sentence $(A \implies B) \implies C$.
  What can you conclude
  about conditionals and the associative property?
  
  完成复合句 $A \implies (B \implies C)$ 和句子 $(A \implies B) \implies C$ 的真值表。关于条件句和结合律，你能得出什么结论？
  
  \wbvfill
  
  \hint{
  No help on this one other than to say that the associative property {\bf does not} hold for implications.
  
  除了说明蕴涵{\bf 不}满足结合律之外，这个问题没有其他帮助。
  \vfill
  
  }
  
  
  \hintspagebreak
  
  \item Determine a sentence using the {\em and} connector ($\land$) that
  gives the negation of $A \implies B$.
  
  使用{\em 与}联结词($\land$)确定一个句子，该句子是 $A \implies B$ 的否定。
  \wbvfill
  
  \hint{Hmmm\ldots This will seem like a strange hint, but if you were to hear a kid at the playground say ``Oh yeah?
  Well, I did call your mom a fatty and you still haven't clobbered me! Owww! OWWW!!!
  Stop hitting me!!''
  
  嗯……这提示可能有点奇怪，但如果你在操场上听到一个孩子说：“哦是吗？我确实叫了你妈妈胖子，但你还没揍我！哎哟！嗷！！！别打了！！”
  
  What conditional sentence was he attempting to negate?
  
  他试图否定的是哪个条件句？
  }
  
  \item Rewrite the sentence ``Fix the toilet or I won't pay the rent!'' as
  a conditional.
  
  将句子“修好马桶，否则我不付房租！”改写为条件句。
  \wbvfill
  
  \hint{The way I see it there are eight possible ways to arrange "You fix the toilet" and "I'll pay the rent" (or their respective negations) around an implication arrow.
  Here they all are.  You decide which one sounds best.
  If you fix the toilet, then I'll pay the rent.\newline
  If you fix the toilet, then I won't pay the rent.\newline
  If you don't fix the toilet, I'll pay the rent.\newline
  If you don't fix the toilet, then I won't pay the rent.\newline
  If I payed the rent, then you must have fixed the toilet.\newline
  If I payed the rent, then you must not have fixed the toilet.\newline
  If I didn't pay the rent, then you must have fixed the toilet.\newline
  If I didn't pay the rent, then you must not have fixed the toilet.\newline
  
  在我看来，有八种可能的方式可以将“你修好马桶”和“我会付房租”（或它们各自的否定）围绕一个蕴涵箭头排列。这里是所有的方式。你来决定哪一个听起来最好。
  如果你修好马桶，那么我会付房租。\newline
  如果你修好马桶，那么我不会付房租。\newline
  如果你不修好马桶，我会付房租。\newline
  如果你不修好马桶，那么我不会付房租。\newline
  如果我付了房租，那么你一定修好了马桶。\newline
  如果我付了房租，那么你一定没有修好马桶。\newline
  如果我没有付房租，那么你一定修好了马桶。\newline
  如果我没有付房租，那么你一定没有修好马桶。\newline
  
  Some of those are truly strange\ldots
  
  其中一些真的很奇怪……
  }
  
  \workbookpagebreak
  
  \item Why is it that the sentence ``If 
  pigs can fly, I am the king
  of Mesopotamia.'' true?
  
  为什么“如果猪会飞，我就是美索不达米亚的国王”这句话是真的？
  
  \wbvfill
  
  \hint{Unless we're talking about some celebrity bringing their pet Vietnamese pot-bellied pig into first class with them, or possibly a catapult of some type...  The antecedent (the if part) is false, so Yay!
  I AM the king of Mesopotamia!! Whoo-hooh! What? I'm not? Oh.  But the if-then sentence is true.
  Bummer.
  
  除非我们谈论的是某个名人把他们的宠物越南大肚猪带进头等舱，或者可能是某种弹射器……前件（如果部分）是假的，所以耶！我就是美索不达米亚的国王！！哇哦！什么？我不是？哦。但这个如果-那么句子是真的。真扫兴。
  }
  
  \item Express the statement $A \implies B$ using the Peirce arrow and/or the
  Scheffer stroke.
  (See Exercise~\ref{ex:nand_nor} in the previous section.)
  
  使用皮尔斯箭头和/或谢弗竖线来表达陈述 $A \implies B$。（参见上一节的练习~\ref{ex:nand_nor}。）
  
  \wbvfill
  
  \hint{You'll want to use $\vert$, the Scheffer stroke, aka NAND, because it's truth table contains three $T$'s and one $\phi$ -- you'll just need to figure out which of its inputs to negate so as to make that one $\phi$ occur in the second row of the table instead of the first.
  
  你会想使用 $\vert$，即谢弗竖线，也就是与非门，因为它的真值表包含三个T和一个$\phi$——你只需要弄清楚应该否定哪个输入，以使那个唯一的$\phi$出现在表的第二行而不是第一行。
  }
  
  
  
  \item Find the contrapositives of the following sentences.
  
  找出下列句子的逆否命题。
  \begin{enumerate}
    \item \wbitemsep If you can't do the time, don't do the crime.
    
    如果你承担不了后果，就不要做坏事。
    \item \wbitemsep If you do well in school, you'll get a good job.
    
    如果你在学校表现好，你就会找到一份好工作。
    \item \wbitemsep If you wish others to treat you in a certain way, you must 
      treat others in that fashion.
      
    如果你希望别人以某种方式对待你，你必须以那种方式对待别人。
    \item \wbitemsep If it's raining, there must be clouds.
    
    如果下雨，就一定有云。
    \item \wbitemsep If $a_n \leq b_n$, for all $n$ and $\sum_{n=0}^\infty b_n$ is a 
  convergent series, then $\sum_{n=0}^\infty a_n$ is a convergent series.
  
  如果对于所有的 $n$ 都有 $a_n \leq b_n$，并且 $\sum_{n=0}^\infty b_n$ 是一个收敛级数，那么 $\sum_{n=0}^\infty a_n$ 也是一个收敛级数。
  \end{enumerate}
  
  %\wbvfill
  
  \hint{
  \begin{enumerate}
  \item If you do the crime, you must do the time.
  
  如果你做了坏事，你就必须承担后果。
  \item If you don't have a good job, you must've done poorly in school.
  
  如果你没有一份好工作，你一定是在学校表现不好。
  \item If you don't treat others in a certain way, you can't hope for others to treat you in that fashion,
  
  如果你不以某种方式对待他人，你就不能指望他人以那种方式对待你。
  \item If there are no clouds, it can't be raining.
  
  如果没有云，就不可能下雨。
  \item If  $\sum_{n=0}^\infty a_n$ is not a convergent series, then either $a_n \leq b_n$, for some $n$ or 
  $\sum_{n=0}^\infty b_n$ is not a convergent series.
  
  如果 $\sum_{n=0}^\infty a_n$ 不是一个收敛级数，那么要么对于某个 $n$ 有 $a_n > b_n$[注意：原文此处应为>], 要么 $\sum_{n=0}^\infty b_n$ 不是一个收敛级数。
  \end{enumerate}
  }
  \rule{0pt}{0pt}
  
  %\wbvfill
  
  \workbookpagebreak
  
  \item What are the converse and inverse of ``If you watch my back, I'll 
  watch your back.''?
  
  “如果你掩护我，我也会掩护你”的逆命题和否命题是什么？
  \wbvfill
  
  \hint{
  The converse is ``If I watch your back, then you'll watch my back.''  (Sounds a little dopey doesn't it -- likes its sort of a wishful thinking\ldots)
  The inverse is ``If you don't watch my back, then I won't watch your back.''  (Sounds less vapid, but it means the same thing\ldots)
  
  逆命题是“如果我掩护你，那么你也会掩护我。”（听起来有点傻，不是吗——有点像一厢情愿……）
  否命题是“如果你不掩护我，那么我也不会掩护你。”（听起来不那么空洞，但意思是一样的……）
  }
  
  
  
  \item The integral test in Calculus is used to determine whether an
  infinite series converges or diverges:   Suppose that $f(x)$ is a positive,
  decreasing, 
  real-valued function with $\lim_{x \longrightarrow \infty} f(x) = 0$, if
  the improper integral
  $\int_0^\infty f(x)$ has a finite value, then the infinite series 
  $\sum_{n=1}^\infty f(n)$ converges.
  The integral test should be envisioned by letting the series correspond
  to a right-hand Riemann sum for the integral, since the function is decreasing,
  a right-hand Riemann sum is an underestimate for the value of the integral,
  thus
  
  微积分中的积分判别法用于判断一个无穷级数是收敛还是发散：假设 $f(x)$ 是一个正的、递减的实值函数，且 $\lim_{x \longrightarrow \infty} f(x) = 0$，如果反常积分 $\int_0^\infty f(x)$ 有一个有限值，那么无穷级数 $\sum_{n=1}^\infty f(n)$ 收敛。积分判别法可以通过将级数对应于积分的右黎曼和来形象地理解，因为函数是递减的，右黎曼和是积分值的下估计，因此
  
  \[ \sum_{n=1}^\infty f(n) < \int_0^\infty f(x).
  \]
  
  Discuss the meanings of and (where possible) provide justifications for
  the inverse, converse and contrapositive of the conditional statement 
  in the integral test.
  
  讨论积分判别法中条件陈述的否命题、逆命题和逆否命题的含义，并在可能的情况下为其提供理由。
  \wbvfill
  
  \hint{
  The inverse says -- if the integral isn't finite, then the series doesn't converge.
  You can cook-up a function that shows this to be false by (for example) creating one with vertical asymptotes that occur in between the integer $x$-values.
  Even one such pole can be enough to make the integral go infinite.
  The converse says that if the series converges, the integral must be finite.
  The counter-example we just discussed would work here too.
  
  否命题说——如果积分不是有限的，那么级数就不收敛。你可以构造一个函数来证明这是错误的，例如，创建一个在整数x值之间有垂直渐近线的函数。即使只有一个这样的极点也足以使积分变为无穷大。
  逆命题说，如果级数收敛，那么积分必须是有限的。我们刚才讨论的反例在这里也适用。
  
  The contrapositive says that if the series doesn't converge, then the integral must not be finite.
  If we were allowed to use discontinuous functions, it isn't too hard to come up with an $f$ that actually has zero area under it -- just make f be identically zero except at the integer x-values where it will take the same values as the terms of the series.
  But wait, the function we just described isn't ``decreasing'' -- which is probably why that hypothesis was put in there!
  
  逆否命题说，如果级数不收敛，那么积分必定不是有限的。如果我们被允许使用不连续函数，不难想出一个其下方实际面积为零的 $f$ ——只需让f在除了整数x值之外的地方恒为零，在整数x值处取与级数项相同的值即可。但是等等，我们刚才描述的函数不是“递减”的——这可能就是为什么把那个假设放在那里的原因！
  }
  
  \rule{0pt}{0pt}
  
  \wbvfill
  
  \workbookpagebreak
  
  \item On the Island of Knights and Knaves (see page~\pageref{IKK}) you encounter two individuals named Locke and Demosthenes.
  Locke says, ``Demosthenes is a knave.'' \newline
  Demosthenes says ``Locke and I are knights.''
  
  在骑士与无赖岛上（见第~\pageref{IKK}页），你遇到了两个名叫洛克和德摩斯梯尼的人。
  洛克说：“德摩斯梯尼是个无赖。”\newline
  德摩斯梯尼说：“洛克和我是骑士。”
  
  Who is a knight and who a knave?
  
  谁是骑士，谁是无赖？
  \wbvfill
  
  \hint{Could Demosthenes be telling the truth?
  
  德摩斯梯尼可能在说真话吗？}
  
  \end{enumerate}