\begin{enumerate}
    \item Do the algebra (and show all your work!) to prove that invariant
    defined in this section actually has the value 1 for the set of all the
    men occupying the $x$-axis and the lower half-plane.

    \noindent 请进行代数运算（并展示所有步骤！）来证明本节中定义的不变量对于占据x轴和下半平面的所有男性集合确实具有值1。
    \wbvfill
    
    \workbookpagebreak
    
    \item ``Escape of the clones'' is a  nice puzzle, originally proposed by Maxim Kontsevich.
    
    \noindent “克隆人逃脱”是一个很好的谜题，最初由马克西姆·康采维奇提出。
    The game
    is played on an infinite checkerboard restricted to the first quadrant -- that is the squares may be 
    identified with points having integer coordinates $(x,y)$ with $x>0$ and $y>0$.

    游戏在一个仅限于第一象限的无限棋盘上进行——也就是说，棋盘格可以被识别为具有整数坐标 $(x,y)$ 且 $x>0, y>0$ 的点。

    The ``clones'' are markers
    (checkers, coins, small rocks, whatever\ldots) that can move in only one fashion -- if the squares immediately
    above and to the right of a clone are empty, then it can make a ``clone move.''   The clone moves one space
    up and a copy is placed in the cell one to the right.

    \noindent “克隆人”是标记物（棋子、硬币、小石子等等……），它们只能以一种方式移动——如果一个克隆人正上方和正右方的格子是空的，那么它就可以进行一次“克隆移动”。克隆人向上移动一格，同时一个复制品被放置在右边一格的单元格中。

    We begin with three clones occupying cells $(1,1), (2,1)$ and $(1,2)$ -- we'll refer to those three checkerboard squares as ``the prison.''  The question is this:  can these
    three clones escape the prison?

    我们开始时有三个克隆人占据着单元格 $(1,1), (2,1)$ 和 $(1,2)$ ——我们将这三个棋盘格称为“监狱”。问题是：这三个克隆人能逃出监狱吗？

    You must either demonstrate a sequence of moves that frees all three clones or provide an argument that the task is impossible.

    你必须要么展示一个能让所有三个克隆人都获得自由的移动序列，要么提供一个论证说明这个任务是不可能的。
    \wbvfill
    
    \end{enumerate}
    
    %% Emacs customization
    %% 
    %% Local Variables: ***
    %% TeX-master: "GIAM-hw.tex" ***
    %% comment-column:0 ***
    %% comment-start: "%% "  ***
    %% comment-end:"***" ***
    %% End: ***