\begin{enumerate}

    \item How many quantifiers (and what sorts) are in the following sentence?
    ``Everybody has \emph{some} friend that thinks they know everything about 
    a sport.''
    
    下面这个句子中有多少个量词（以及是哪种量词）？“每个人都有\emph{某个}朋友，认为自己了解一项运动的所有事情。”
      
    \wbvfill
    
    \hint{Four.
    
    四个。}
    
    \item The sentence ``Every metallic element is a solid at room temperature.'' 
    is false. Why?
    
    “每种金属元素在室温下都是固体” 这句话是错误的。为什么？
    
    \wbvfill
    
    \hint{The chemical symbol for an element that is an exception is Hg which stands for "Hydro-argyrum" it is also known as "liquid silver" or "quick silver".
    
    作为例外的元素的化学符号是Hg，它代表“水银”，也被称为“液态银”或“快银”。}
    
    \item The sentence ``For every pair of (distinct) real numbers there is 
    another real number between them.'' is true. Why?
    
    “对于每一对（不同的）实数，它们之间都存在另一个实数” 这句话是正确的。为什么？
    
    \wbvfill
    
    \hint{Think about this: is there any way to (using a formula) find a number that lies in between two other numbers?
    
    想一想：有没有什么方法（用一个公式）可以找到一个位于另外两个数之间的数？}
    
    \item Write your own sentences containing four quantifiers. One
    sentence in which the quantifiers appear ($\forall \exists \forall \exists$)
    and another in which they appear ($\exists \forall \exists \forall$).
    
    写出你自己的包含四个量词的句子。一个句子中量词以($\forall \exists \forall \exists$)的顺序出现，另一个句子中以($\exists \forall \exists \forall$)的顺序出现。
    \wbvfill
    
    \hint{You're on your own here.  Be inventive!
    
    这里要靠你自己了。发挥创造力！}
    
    \end{enumerate}