\begin{enumerate}
  \item Determine the number of entries in the following sequences.
  
  \noindent 确定以下序列中的项数。
  \begin{enumerate}
    \item \wbitemsep $(999, 1000, 1001, \ldots  2006)$
    \item \wbitemsep $(13, 15, 17, \ldots 199)$
    \item \wbitemsep $(13, 19, 25, \ldots 601)$
    \item \wbitemsep $(5, 10, 17, 26, 37, \ldots 122)$
    \item \wbitemsep $(27, 64, 125, 216, \ldots 8000)$
    \item \wbitemsep $(7, 11, 19, 35, 67, \ldots 131075)$
    \end{enumerate}
  
  \workbookpagebreak
  
  \item How many ``full houses'' are there in Yahtzee? (A full house is a pair
  together with a three-of-a-kind.)
  
  \noindent Yahtzee骰子游戏中有多少种“葫芦”？（“葫芦”是指一对和三条的组合。）
  
  \wbvfill
  
  \item In how many ways can you get ``two pairs'' in Yahtzee?
  
  \noindent 在Yahtzee骰子游戏中有多少种方式可以得到“两对”？
  \wbvfill
  
  \item Prove that the binomial coefficients $\displaystyle \binom{n+k-1}{k}$
  and $\displaystyle \binom{n+k-1}{n-1}$ are equal.
  
  \noindent 证明二项式系数 $\displaystyle \binom{n+k-1}{k}$ 和 $\displaystyle \binom{n+k-1}{n-1}$ 相等。
  \wbvfill
  
  \workbookpagebreak
  
  \item The ``Cryptographer's alphabet'' is used to supply small examples
  in coding and cryptography. It consists of the first 6 letters, $\{a, b, c, d, e, f\}$. How many ``words'' of length up to 6 can be made with this 
  alphabet? (A word need not actually be a word in English, for example 
  both ``fed'' and ``dfe'' would be words in the sense we are using the term.)
  
  \noindent “密码学家字母表”用于提供编码和密码学中的小例子。它由前6个字母组成，即 $\{a, b, c, d, e, f\}$。用这个字母表可以组成多少个长度不超过6的“单词”？（一个“单词”不一定非得是英语单词，例如，“fed”和“dfe”在我们使用的意义上都是单词。）
  
  \wbvfill
  
  \item How many ``words'' are there of length 4, with distinct letters from the 
  Cryptographer's alphabet, in which the letters appear in increasing order 
  alphabetically? (``Acef'' would be one such word, but ``cafe'' would not.)
  
  \noindent 从密码学家字母表中选取不同的字母，可以组成多少个长度为4且字母按字母顺序递增的“单词”？（例如，“acef”是这样的一个词，但“cafe”不是。）
  
  \wbvfill
  
  \item How many ``words'' are there of length 4 from the 
  Cryptographer's alphabet, with repeated letters allowed,
   in which the letters appear in non-decreasing order alphabetically?
  
   \noindent 从密码学家字母表中（允许重复字母）可以组成多少个长度为4且字母按字母顺序非递减排列的“单词”？
  \wbvfill
  
  \workbookpagebreak
  
  \item How many subsets does a finite set have?
  
  \noindent 一个有限集有多少个子集？
  
  \wbvfill
  
  \item How many handshakes will transpire when $n$ people first meet?
  
  \noindent 当$n$个人初次见面时，会发生多少次握手？
  \wbvfill
  
  \item How many functions are there from a set of size $n$ to a set of size $m$?
  
  \noindent 从一个大小为$n$的集合到一个大小为$m$的集合，有多少个函数？
  \wbvfill
  
  \item How many relations are there from a set of size $n$ to a set of size $m$?
  
  \noindent 从一个大小为$n$的集合到一个大小为$m$的集合，有多少个关系？
  \wbvfill
  
  \workbookpagebreak
  
  \end{enumerate}
  
  %% Emacs customization
  %% 
  %% Local Variables: ***
  %% TeX-master: "GIAM-hw.tex" ***
  %% comment-column:0 ***
  %% comment-start: "%% "  ***
  %% comment-end:"***" ***
  %% End: ***