\begin{enumerate}

    \item A walking tour of K\"{o}nigsberg such as is described in this section,
    or more generally, a circuit through an arbitrary graph that crosses each
    edge precisely once and begins and ends at the same node is known as
    an \index{Eulerian circuit} \emph{Eulerian circuit}.  An \index{Eulerian
    path} \emph{Eulerian path} also crosses every edge of a graph exactly
    once but it begins and ends at distinct nodes.  For each of the following
    graphs determine whether an Eulerian circuit or path is possible, and if so,
    draw it.
    
    \noindent 如本节所述的柯尼斯堡漫步，或者更一般地，在一个任意图中，精确地穿过每条边一次并起止于同一节点的回路，被称为\index{Eulerian circuit}\emph{欧拉回路}。而\index{Eulerian path}\emph{欧拉路径}也精确地穿过图的每条边一次，但它的起点和终点是不同的节点。对于下面的每一个图，判断是否存在欧拉回路或欧拉路径，如果存在，请画出它。
    
    \begin{center}
    \input{figures/Euler_circuit_problems_a.tex}
    \end{center}
    
    \begin{center}
    \input{figures/Euler_circuit_problems_b.tex}
    \end{center}
    
    \item Complete the proof of the fact that ``Every graph has an even number
    of odd nodes.''
    
    \noindent 完成“每个图都有偶数个奇数度节点”这一事实的证明。
    
    \wbvfill
    
    \item Provide an argument as 
    to why an $8 \times 8$ chessboard with 
    two squares pruned from diagonally opposite corners cannot be tiled
    with dominoes.
    
    \noindent 请给出一个论证，说明为什么一个$8 \times 8$的棋盘，在对角线两端各去掉一个方格后，无法用多米诺骨牌完全覆盖。
    
    \wbvfill
    
    \workbookpagebreak
    
    \item Prove that, if $n$ is odd, any $n \times n$ chessboard with 
    a square the same color as one of its corners pruned can be tiled by
    dominoes.
    
    \noindent 证明，如果$n$是奇数，任何$n \times n$的棋盘，在去掉一个与其角格颜色相同的方格后，可以用多米诺骨牌完全覆盖。
    \wbvfill
    
    \item The five \index{tetromino} tetrominoes (familiar to players of the video game
    Tetris) are relatives of dominoes made up of four small squares.
    
    \noindent 五个\index{tetromino}四格骨牌（俄罗斯方块玩家很熟悉）是多米诺骨牌的亲戚，由四个小方格组成。
    \begin{center}
    \input{figures/five_tetrominoes.tex}
    \end{center}
    
    \noindent All together these five tetrominoes contain 20 squares
    so it is conceivable that they could be used to tile a $4 \times 5$
    chessboard. Prove that this is actually impossible.
    
    \noindent 这五个四格骨牌总共包含20个方格，所以可以想象它们可以用来铺满一个$4 \times 5$的棋盘。证明这实际上是不可能的。
    
    \wbvfill
    
    \workbookpagebreak
    
    \item State necessary and sufficient conditions for the existence of
    an Eulerian circuit in a graph.
    
    \noindent 陈述图中存在欧拉回路的充要条件。
    \wbvfill
    
    \item  State necessary and sufficient conditions for the existence of
    an Eulerian path in a graph.
    
    \noindent 陈述图中存在欧拉路径的充要条件。
    \wbvfill
    
    \newpage
    
    \item Construct magic squares of order 4 and 5.
    
    \noindent 构建4阶和5阶的幻方。
    
    \wbvfill
    
    \workbookpagebreak
    
    \item A magic hexagon of order 2 would consist of filling-in
    the numbers from 1 to 7 in the hexagonal array below. The magic
    condition means that each of the 9 ``lines'' of adjacent hexagons
    would have the same sum.  Is this possible?
    
    \noindent 一个2阶的幻六边形需要将数字1到7填入下面的六边形阵列中。幻方的条件意味着每9条相邻六边形的“线”上的数字之和都相同。这可能吗？
    \begin{center}
    \input{figures/magic_hexagon.tex}
    \end{center}
    
    \wbvfill
    
    \item Is there a magic hexagon of order 3?
    
    \noindent 存在3阶的幻六边形吗？
    
    \wbvfill
    
    \end{enumerate}
    
    
    
    %% Emacs customization
    %% 
    %% Local Variables: ***
    %% TeX-master: "GIAM-hw.tex" ***
    %% comment-column:0 ***
    %% comment-start: "%% "  ***
    %% comment-end:"***" ***
    %% End: ***