\begin{enumerate}

    \item The statement that there are two non-bald New Yorkers with
    the same number of hairs on their heads requires some careful 
    estimates to justify it. Please justify it.
    
    \noindent “纽约市有两个非秃头的人头发数量相同”这一说法需要一些仔细的估计来证明。请证明之。
    
    \wbvfill
    
    \item A mathematician, who always rises earlier than her spouse, has
    developed a scheme -- using the pigeonhole principle -- to ensure that
    she always has a matching pair of socks. She keeps only blue socks, green 
    socks and
    black socks in her sock drawer -- 10 of each. So as not to wake her 
    husband she must
    select some number of socks from her drawer in the early morning dark
    and take them with her to the adjacent bathroom where she dresses. What number of socks does she choose?
    
    \noindent 一位总比配偶早起的数学家，设计了一个方案——利用鸽巢原理——来确保她总能拿到一双配对的袜子。她的袜筒里只有蓝色、绿色和黑色的袜子——每种颜色10只。为了不吵醒丈夫，她必须在清晨的黑暗中从抽屉里拿出一定数量的袜子，带到隔壁的浴室里穿。她需要选择多少只袜子？
    
    \wbvfill
    
    \workbookpagebreak
    
    \item If we select $1001$ numbers from the set $\{1, 2, 3, \ldots, 2000\}$
    it is certain that there will be two numbers selected such that one divides
    the other. We can prove this fact by noting that every number in the given
    set can be expressed in the form $2^k \cdot m$ where $m$ is an odd number
    and using the pigeonhole principle. Write-up this proof.
    
    \noindent 如果我们从集合 $\{1, 2, 3, \ldots, 2000\}$ 中选取 $1001$ 个数，那么可以肯定，选出的数中必有两个数，其中一个能整除另一个。我们可以通过指出给定集合中的每个数都可以表示为 $2^k \cdot m$ 的形式（其中 $m$ 是一个奇数）并利用鸽巢原理来证明这一事实。请写出这个证明。
    
    \wbvfill
    
    \item Given any set of $53$ integers, show that there are two of them
    having the property 
    that either their sum or their difference is evenly divisible by $103$.
    
    \noindent 给定任意53个整数的集合，证明其中必有两个整数，它们的和或差能被103整除。
    \wbvfill
    
    \workbookpagebreak
    
    \item Prove that if $10$ points are placed inside a square of side length 3,
    there will be 2 points within $\sqrt{2}$ of one another.
    
    \noindent 证明：如果在边长为3的正方形内放置10个点，则必有两个点之间的距离在 $\sqrt{2}$ 以内。
    \wbvfill
    
    \item Prove that if $10$ points are placed inside an equilateral triangle
    of side length 3, there will be 2 points within $1$ of one another.
    
    \noindent 证明：如果在边长为3的等边三角形内放置10个点，则必有两个点之间的距离在1以内。
    \wbvfill
    
    \workbookpagebreak
    
    \item Prove that in a simple graph (an undirected graph with no 
    loops or parallel edges) having $n$ nodes, there must be two nodes 
    having the same degree.
    
    \noindent 证明在一个有 $n$ 个节点的简单图（无环或平行边的无向图）中，必定有两个节点具有相同的度。
    \wbvfill
    
    \workbookpagebreak
    
    \end{enumerate}
    
    
    %% Emacs customization
    %% 
    %% Local Variables: ***
    %% TeX-master: "GIAM-hw.tex" ***
    %% comment-column:0 ***
    %% comment-start: "%% "  ***
    %% comment-end:"***" ***
    %% End: ***